RVD2: An ultra-sensitive variant detection model for low-depth heterogeneous next-generation sequencing data

### 2015-03-09 doc/bioinformatics2014/revision2/document.tex
Updated PAXIP1 results

\vspace{-10pt}
\subsection{HCC1187 primary ductal carcinoma sample}\label{sec:brca}
\begin{figure*}[!hbpt]
\centering
\vspace{-10pt}
\includegraphics[width=0.68\textwidth]{pdf_figs/HCC1187_MuBarPlot.pdf}
\caption{Estimated minor allele fraction for germline and somatic mutations called by RVD2 in the 44kbp PAXIP1 gene. Blue diamonds ($\diamond$) indicates germline mutations, where $\mu^{\text{control}}$ is significantly different from the reference sequence. Red stars (*) indicates somatic mutations, where $\mu^{\text{case}}$ is significantly different from $ \mu^{\text{control}}$. The  vertical lines represent 95\% credible interval around posterior mean MAF. Five positions are common population SNPs according to dbSNPv138, and the identities are shown below the positions.}
\vspace{-10pt}
\label{fig:brca_MAF}
\end{figure*}
% figure 5 generated from 2014-03-24_germline_and_somatic_test_correction_no_subclassification

\begin{figure*}[!pthb]
\vspace{-10pt}
    \centering
    \subfloat[\label{fig:brca_dot:a}]{{\includegraphics[width=0.7\textwidth]{pdf_figs/HCC1187_dotplot.pdf} }}%
    %
    \subfloat[\label{fig:brca_dot:b}]{{\includegraphics[width=0.18\textwidth]{pdf_figs/position_lookup_chart.pdf} }}%
    \caption{(a) Positions called by VarScan2-somatic, muTect, RVD2 and Strelka in the 44kbp PAXIP1 gene from chr7:154,735,400 to chr7:154,794,682. The positions are sorted by index (correspondance to genomic positions shown in Supplementary Table 1) (b) Read counts for each base for positions called by RVD2 and muTect from raw pileup data.}%
    \label{fig:brca_dot}%
\vspace{-10pt}
\end{figure*}

>>>>

\vspace{-10pt}
\subsection{HCC1187 primary ductal carcinoma sample}\label{sec:brca}
\begin{figure*}[!hbpt]
\centering
\vspace{-10pt}
\includegraphics[width=0.9\textwidth]{pdf_figs/HCC1187_MuBarPlot.pdf}
\caption{Estimated minor allele fraction for germline and somatic mutations called by RVD2 in the 59kbp PAXIP1 gene. Blue diamonds ($\diamond$) indicates germline mutations, where $\mu^{\text{control}}$ is significantly different from the reference sequence. Red stars (*) indicates somatic mutations, where $\mu^{\text{case}}$ is significantly different from $ \mu^{\text{control}}$. The  vertical lines represent 95\% credible interval around posterior mean MAF. Ten positions are common population SNPs according to dbSNPv138, and the identities are shown below the positions.}
\vspace{-10pt}
\label{fig:brca_MAF}
\end{figure*}
% figure 5 generated from 2014-03-24_germline_and_somatic_test_correction_no_subclassification

\begin{figure*}[!pthb]
\vspace{-10pt}
    \centering
    \subfloat[\label{fig:brca_dot:a}]{{\includegraphics[width=0.8\textwidth]{pdf_figs/HCC1187_dotplot.pdf} }}%
    %
    \subfloat[\label{fig:brca_dot:b}]{{\includegraphics[width=0.21\textwidth]{pdf_figs/position_lookup_chart.pdf} }}%
    \caption{(a) Positions called by VarScan2-somatic, muTect, RVD2 and Strelka in the 59kbp PAXIP1 gene from chr7:154,735,400 to chr7:154,794,682. The positions are sorted by index (correspondance to genomic positions shown in Supplementary Table 1) (b) Read counts for each base for positions called by RVD2 and muTect from raw pileup data.}%
    \label{fig:brca_dot}%
\vspace{-10pt}
\end{figure*}
